### 2021-09-28 papers/thesis/resubmitted/ch2-spherical-harmonics/spherical-harmonics.tex
Added TJx etc. to notation index

The Jacobi matrices are then defined according to the matrices $\tangentjacobi_x, \tangentjacobi_y, \tangentjacobi_z$ satisfying

>>>>

The Jacobi matrices are then defined according to the matrices \nomenclature[JT]{$\tangentjacobi_x, \tangentjacobi_y, \tangentjacobi_z$}{The Jacobi matrices for the tangent bundle VSH basis} $\tangentjacobi_x, \tangentjacobi_y, \tangentjacobi_z$ satisfying
